### 2023-03-16 code/analysis_code/analysis_README.Rmd
editing for grammer and flow

This folder contains code for analyzing cleaned data sets on Tempertature, Salinity, Dust, and Vibrio counts. `daily.qmd` assesses Vibrio counts over the daily time series, `dust.qmd` pertains to the dust concentrations sourced from NRL, `dust_and_copies.qmd` look at the former two data sets in tandem, and `env_par.qmd` looks at temperature and salinity.

>>>>

This folder contains code for analyzing cleaned data sets and aids in visualization of parameters of interest.\
(1) The dust subfolder contains `daily_dust.qmd`, which looks at dust concentration over the daily time series. It also contains `dust_and_copies.qmd` which combine Vibrio enumeration with dust data.\
(2) The env sub-folder contains `env_par.qmd` that examines temperature and salinity over the time series.\
(3) The qPCR sub-folder contains `daily_qmd` that has data on Vibrio enumeration. This is also seen in the `dust_and_copies.qmd` in the dust subfolder \
(4) The stats folder contains `dust_copies_stats.qmd` that runs models on variables of interest. \

### 2023-03-16 code/wrangling_code/wrangling_README.Rmd
editing for grammer and flow

The folder contains various cleaning codes for data sets on environmental parameters (dust, temperature, salinity), and total Vibrio counts in sea surface waters.

>>>>

The folder contains various cleaning codes:\
(1) `dust.qmd`: This code takes dust concentration data from NRL and cleans it. Steps include, switching to the correct timezone, creating concentration sums per day, as well as combining the dust data set with the vibrio enumeration data set.\
(2) `total_copies_calculator.qmd`: This script is for cleaning qPCR results on Total Vibrio enumeration. It takes Cq value outputs from the CFX (qPCR machine) and computes it to copies of gene targets of Vibrio. The data set contains a daily and monthly time series. We will be examining daily.\
(3) `df_master.qmd`: This script combines the three clean data sets for dust concentration, copies per mL, and environmental parameters

### 2023-03-16 data/processed_data/processed_data_README.Rmd
editing for grammer and flow

This folder contains processed data that has been cleaned from code in the `wrangling` folder.\
(1) `total_clean_copies`: Vibrio enumeration (as copies per mL) across time series.\
(2) `dust_clean.rds`: Cleaned dust data
(3) `ysi_2.csv`: Environmental parameter data
(4) `tx_master.csv` which is a compilation of all relevant data. 
(5)`dust_master.csv`: Manually created dust data examining different time points, sums, avereages (helpful for statistics)

>>>>

This folder contains processed data that has been cleaned from code in the `wrangling` folder.\
(1) `total_clean_copies`: Vibrio enumeration (as copies per mL) across time series.\
(2) `dust_clean.rds`: Cleaned dust data
(3) `ysi_2.csv`: Environmental parameter data-- did not need cleaning
(4) `tx_master.csv` which is a compilation of all relevant data. 
(5)`dust_master.csv`: Manually created dust data examining different dust permutations: time points, sums, avereages (helpful for statistics)
